Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-07-07 paper/tool.tex
Tool section: Fix broken macros, references, and citations

\newcommand{\pwter}{{\sc PwTer}}

\section{\pwter: automatic litmus test evaluator}
\label{sec:tool}

\pwter automatically and exhaustively calculates the allowed outcomes of litmus tests for the PwT, PwT-po and PwT-C11 models. It is built in OCaml, and uses Z3~\cite{???} to judge the truth of predicates constructed by the models. \pwter obviates the need for error-prone hand evaluation.

\pwter allows several modes of evaluation: it can evaluate the rules of Fig.~\ref{fig:seq}, implementing PwT; it can generate program order according to Section~\ref{sec:c11}, implementing PwwT-po; and similar to \MRD~\cite{DBLP:conf/esop/PaviottiCPWOB20}, it can construct C11-style pre-executions and filter them according to the rules of C11.
Our choice of C11 rules is careful: we take the rules of RC11~\cite{DBLP:conf/pldi/LahavVKHD17}, but we replace the overly strong No-Thin-Air restriction $\text{acyclic}(\rrf\cup\rpox)$ with $\text{acyclic}(\rrf\cup\lt)$. 
This is a more precise categorisation of thin-air behavior, and it allows aggressive compiler optimisations which would be erroneously forbidden by RC11's original No-Thin-Air axiom.
We show \pwter in action in Fig.~\ref{fig:tool}.
Finally, \pwter also allows us to toggle the completeness check of~\ref{def:complete}, providing an interface for understanding how fragments of code might compose by exposing preconditions and termination conditions which are not yet tautologies.

@@

%% [Simon] I am not a fan of how this looks on the page.
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.75\textwidth]{tool.png}
  \Description{Image shows tool running on a Mac. Java Causality Test Case 1 is printed, followed by an invocation of the tool as {\tt ./pomsets.exe --check --complete data/tests/jctc/jctc1.lit}, which shows that the tool passes the assertion listed in the test.}
  \caption{\label{fig:tool} Example output of tool, validating TC1~\cite{PughWebsite}.}
\end{center}
\end{figure}

>>>>

\section{\PwTerTITLE: automatic litmus test evaluator}
\label{sec:tool}

\PwTer{} automatically and exhaustively calculates the allowed outcomes of litmus tests for the PwT, PwT-po and PwT-C11 models. It is built in OCaml, and uses Z3~\cite{Z3Solver} to judge the truth of predicates constructed by the models. \PwTer{} obviates the need for error-prone hand evaluation.

\PwTer{} allows several modes of evaluation: it can evaluate the rules of Fig.~\ref{fig:seq}, implementing PwT; it can generate program order according to Section~\ref{sec:c11}, implementing PwwT-po; and similar to \MRD~\cite{DBLP:conf/esop/PaviottiCPWOB20}, it can construct C11-style pre-executions and filter them according to the rules of C11.
Our choice of C11 rules is careful: we take the rules of RC11~\cite{DBLP:conf/pldi/LahavVKHD17}, but we replace the overly strong No-Thin-Air restriction $\text{acyclic}(\rrf\cup\rpox)$ with $\text{acyclic}(\rrf\cup\lt)$. 
This is a more precise categorisation of thin-air behavior, and it allows aggressive compiler optimisations which would be erroneously forbidden by RC11's original No-Thin-Air axiom.
We show \PwTer{} in action in Fig.~\ref{fig:tool}.
Finally, \PwTer{} also allows us to toggle the complete check of~\ref{def:pomset}, providing an interface for understanding how fragments of code might compose by exposing preconditions and termination conditions which are not yet tautologies.

@@

%% [Simon] I am not a fan of how this looks on the page.
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.75\textwidth]{tool.png}
  \Description{Image shows tool running on a Mac. Java Causality Test Case 1 is printed, followed by an invocation of the tool as {\tt ./pomsets.exe --check --complete data/tests/jctc/jctc1.lit}, which shows that the tool passes the assertion listed in the test.}
  \caption{\label{fig:tool} Example output of \PwTer, validating TC1~\cite{PughWebsite}.}
\end{center}
\end{figure}
